Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-24 prop_iop.tex
prop_iop.tex Split Appendix D into Appendix D and E...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}

\subsection{From Real-valued to Interval-valued}

@@

\subsubsection{Convex but Infinite Number of Intervals}

@@

\subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule}

@@

\subsection{From Interval-valued to Real-valued}

Previously we discussed how to construct a quantum IVPM from a quantum
real-valued probability measure; we then switch our focus to how to
construct a quantum real-valued probability measure from a special
kind of quantum IVPMs.

\begin{definition}\label{def:delta-deterministic}An interval-valued
probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\left(1/n,\delta\right)$-deterministic if for every $\left[l,r\right]\in\mathscr{I}$,
there is a $k\in\mathbb{Z}$ such that $\left[l,r\right]\subseteq\left[k/n-\delta,k/n+\delta\right]$.\end{definition}

Recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $\left(1,0\right)$-deterministic.
For another example, given a three-dimensional Hilbert space, 
\begin{equation}
\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
\end{equation}
is $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic.
However, we will prove there is generally no $\left(1/n,\delta\right)$-deterministic
probability measures when $\delta$ is much smaller than $1/n$.

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\left(1/n,\delta\right)$-deterministic probability
measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
$\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
is $\left(1/n,0\right)$-deterministic by lemma~\ref{lemma:real2interval}.\end{lemma}

@@

\begin{lemma}If every interval in $\mathscr{I}$ is a singleton set,
given a QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, then
$\mu:\events\rightarrow\left[0,1\right]$defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
is a quantum probability measure.\end{lemma}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{From QRVPM to QIVPM\label{sec:Real-and-Interval}}

@@

\subsection{Convex but Infinite Number of Intervals}

@@

\subsection{Sates Consistent with a QIVPM Induced by the Born Rule}

@@

\section{From Interval-valued to Real-valued}

Previously we discussed how to construct a quantum IVPM from a quantum
real-valued probability measure; we then switch our focus to how to
construct a quantum real-valued probability measure from a special
kind of quantum IVPMs. Since the only properties we use in this section
is whether its interval-valued or real-valued, the results in this
section applies on every subspace of events\nb$\events'$. In particular,
when $\events'$ is commuting, any quantum results will be classical
as shown in theorem~\ref{thm:sub-event-space}.

\begin{definition}\label{def:delta-deterministic}An interval-valued
probability measure\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$
is called $\left(1/n,\delta\right)$-deterministic if for every $\left[l,r\right]\in\mathscr{I}$,
there is a $k\in\mathbb{Z}$ such that $\left[l,r\right]\subseteq\left[k/n-\delta,k/n+\delta\right]$.\end{definition}

Recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $\left(1,0\right)$-deterministic.
For another example, given a three-dimensional Hilbert space, 
\begin{equation}
\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events'\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
\end{equation}
is $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic.
However, we will prove there is generally no $\left(1/n,\delta\right)$-deterministic
probability measures when $\delta$ is much smaller than $1/n$.

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\left(1/n,\delta\right)$-deterministic probability
measure\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
$\mu(P)=k/n$, then $\mu:\events'\rightarrow\left[0,1\right]$ is
a quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
is $\left(1/n,0\right)$-deterministic by lemma~\ref{lemma:real2interval}.\end{lemma}

@@

\begin{lemma}If every interval in $\mathscr{I}$ is a singleton set,
given a QIVPM\nb$\bar{\mu}:\events'\rightarrow\mathscr{I}$, then
$\mu:\events'\rightarrow\left[0,1\right]$defined by $\bar{\mu}\left(P\right)=\left\{ \mu\left(P\right)\right\} $
is a quantum probability measure.\end{lemma}
